Political-support-in-the-United-States

### 2024-03-12 paper/paper.qmd
Update paper.qmd

Talk more about it.

And also planes (@fig-vote). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

Talk way more about it.

@@

>>>>

@@

Through feature selection, the influence of redundant features and noise features is reduced, and the generalization ability of the model is improved. By means of L1 regularization and L2 regularization, the complexity of the model is limited and overfitting is prevented. By integrating the results of multiple classifiers, the accuracy and robustness of the model are improved. By changing the structure of the model, such as increasing the depth of the network, increasing the hidden layer and changing the activation function, the expressibility of the model is improved. By expanding, rotating and scaling the data, the diversity of the data is increased and the generalization ability of the model is improved.
